How much is too much? Item Response Theory procedures to shorten tests

### 2025-02-10 sis2025/LaTex+Package/styles/paper-sis-template.tex
sis

\section{Simulation study}
Va detto da qualche parte che:

>>>>

The meausemrement precision of each item with respect to different levels of the latent trait can be expressed with the so-called \emph{item information functions} (IIFs), which for the 4-PL is formalized as:

\begin{center}
	Formula del 4-PL
\end{center}

The informativeness of each item is strongly influenced by the location of the item on the latent trait with respect to a specific latent trait level $\theta$, its discirminativity, and the probability of lucky guess and careless error. In absence of lucky guess and careless error, the IIF reaches its maximum when the location of the item $b_i$ matches the latent trait level $\theta$, and it decreases as the distance between $b_i$ and $\theta$ increases. Moreover, the higher the discrimination of the item $a_i$, the more informative the item. However, when the lucky guess and careless error are taken into account, the informativeness of the item decreases, and, most importantly, the maximum of the IIF does not corresponds to the item location on the latent trait and it is generally lower.

The \emph{test information function} (TIF) is the sum of the IIFs, such that its shape (i.e., its informativeness with respect to different levels of the latent trait) and its height (i.e., the amount of information for different levels of the latent trait) depend on the distribution of the items on the latent trait. The more the items with high discrimination and low lucky guess and careless error parameters are spread throughout the latent trait, the more the test would be informative of different regions. The more the items have lucky guesses and careless errors, the less the TIF.

\section{Simulation study}
In this study, we operationalized the tiredeness of the individuals as the probability of committing careless error ($1- d_i$ QUESTA è LA PROBABILITà DI NON CARELESS ERROR DEVO SPIEGARE MEGLIO, mi sto incansiandno basta che alla fine sia coerente), such that the more the items in a test, the higher the probability of committing careless mistakes. 
The careless error probability is instrinsically related to the rank of the item in the test, and it increases as the position of the item in the test increases. It increases exponentially with the function SCRIVERE LA FUNZIONE, such that the first administered item has $d_i = 1$ (i.e., does not have a probability of observing an incorrect response given the latent trait level $\theta$)

Va detto da qualche parte che:
